---
title: "Exercise 1"
author: "Danaé Broustail"
format: html
editor: visual
---

## Sampling from log normal distribution

We sample 100 values from the log-normal distribution using the `rlnorm` function with $\mu = 5, \sigma = 0.5$. We set a seed for reproducibility.

```{r}
set.seed(1) 

mu <- 5.
sigma <- 0.5

vec <- rlnorm(100, meanlog = mu, sdlog = sigma)
```

## Plotting sampled values

We create the plots on the linear and log scale.

#### Histogram

We generate the histogram plots for both linear and log scales.

```{r}
library(ggplot2)

# convert to data frame
data <- data.frame(values = vec)

# linear scale
p1 <- ggplot(data, aes(x = values)) + geom_histogram(bins = 30) 
p1 + ggtitle("Histogram of sampled values")

# log scale
p2 <- ggplot(data, aes(x = log(values))) + geom_histogram(bins = 30)
p2 + ggtitle("Histogram of sampled values (log scale)") + xlab("Log of values") 

```

#### Violin plot

We generate the violin plots for both linear and log scales.

```{r}

# linear scale
p1 <- ggplot(data, aes(x = "", y = values)) + geom_violin() 
p1 + xlab("") + ggtitle("Violin plot of sampled values")

# log scale
p2 <- ggplot(data, aes(x = "", y = log(values))) + geom_violin() 
p2 + xlab("") + ggtitle("Violin plot of the log of sampled values")

```

## Mean and standard deviation of sampled values

The mean is `r mean(vec)` and the standard deviation is `r sd(vec)` .
